## Feature Selection: Differential expression

```{r}
omic_dfs <- list(genomic_data, methylation_data, microbiome_data)
diff_dfs <- diff_express(clinical_data_fixed, dfs_omics = omic_dfs, p_val = P)
df_diff_gen <- as.data.frame(t(diff_dfs$diff_dfs[1][[1]]))
df_diff_meth <- as.data.frame(t(diff_dfs$diff_dfs[2][[1]]))
df_diff_micro <- as.data.frame(t(diff_dfs$diff_dfs[3][[1]]))

rm(omic_dfs)
```

## Data Analysis Differential Expression

```{r}
diff_pval_geno <- diff_dfs$top_table[1][[1]] %>% select(c("P.Value"))
diff_pval_meth <- diff_dfs$top_table[2][[1]] %>% select(c("P.Value"))
diff_pval_micro <- diff_dfs$top_table[3][[1]] %>% select(c("P.Value"))

rm(diff_dfs)
```

## Data Analysis Differential Expression: `genomic_data`

```{r, echo=FALSE}
diff_pval_geno[1:10, , drop = F]
```

```{r, echo=FALSE}
write.csv(diff_pval_geno[1:10, , drop = F], file = paste0(PLOTS_DIR, "diff_pval_geno.csv"), row.names = TRUE)
```


## Data Analysis Differential Expression: `methylation_data`

```{r, echo=FALSE}
diff_pval_meth[1:10, , drop = F]
```

```{r, echo=FALSE}
write.csv(diff_pval_meth[1:10, , drop = F], file = paste0(PLOTS_DIR, "diff_pval_meth.csv"), row.names = TRUE)
```

## Data Analysis Differential Expression: `microbiome_data`

```{r, echo=FALSE}
diff_pval_micro[1:10, , drop = F]
```

```{r, echo=FALSE}
write.csv(diff_pval_micro[1:10, , drop = F], file = paste0(PLOTS_DIR, "diff_pval_micro.csv"), row.names = TRUE)

rm(diff_pval_geno, diff_pval_meth, diff_pval_micro)
```

```{r, echo=FALSE}
## Add OS_STATUS variable to df_diff omic dataframes
df_diff_gen$OS_STATUS <- clinical_data_fixed$OS_STATUS
df_diff_meth$OS_STATUS <- clinical_data_fixed$OS_STATUS
df_diff_micro$OS_STATUS <- clinical_data_fixed$OS_STATUS
```

## Create `df_diff` Omic Dataframes + RACE variable

```{r}
df_diffRace_gen <- df_diff_gen
df_diffRace_meth <- df_diff_meth
df_diffRace_micro <- df_diff_micro

data_race <- as.data.frame(clinical_data_fixed$RACE, row.names = row.names(clinical_data_fixed))
data_race$`clinical_data_fixed$RACE` <- as.factor(data_race$`clinical_data_fixed$RACE`)

# One hot encoding
oh_race <- one_hot(as.data.table(data_race))
oh_race <- as.data.frame(oh_race, row.names = row.names(clinical_data_fixed))

df_diffRace_gen <- cbind(df_diffRace_gen, oh_race)
df_diffRace_meth <- cbind(df_diffRace_meth, oh_race)
df_diffRace_micro <- cbind(df_diffRace_micro, oh_race)
```


## Feature Selection: Information Gain Filter (30 features most relevant per omic data frame)

```{r}
df_ig_gen <- informationGain_fs(df_diff_gen, NFEATURES)$df_ig
df_ig_meth <- informationGain_fs(df_diff_meth, NFEATURES)$df_ig
df_ig_micro <- informationGain_fs(df_diff_micro, NFEATURES)$df_ig
```


```{r, echo=FALSE}
result_ig_gen <- informationGain_fs(df_diff_gen, NFEATURES)$result_ig
result_ig_meth <- informationGain_fs(df_diff_meth, NFEATURES)$result_ig
result_ig_micro <- informationGain_fs(df_diff_micro, NFEATURES)$result_ig

write.csv(result_ig_gen[1:10, , drop = F], file = paste0(PLOTS_DIR, "result_ig_gen.csv"), row.names = TRUE)
write.csv(result_ig_meth[1:10, , drop = F], file = paste0(PLOTS_DIR, "result_ig_meth.csv"), row.names = TRUE)
write.csv(result_ig_micro[1:10, , drop = F], file = paste0(PLOTS_DIR, "result_ig_micro.csv"), row.names = TRUE)

rm(result_ig_gen, result_ig_meth, result_ig_micro)
```



## Feature Selection: Information Gain Filter (30 features most relevant per omic + RACE variable data frame)

```{r}
df_ig_genRace <- informationGain_fs(df_diffRace_gen, NFEATURES)$df_ig
df_ig_methRace <- informationGain_fs(df_diffRace_meth, NFEATURES)$df_ig
df_ig_microRace <- informationGain_fs(df_diffRace_micro, NFEATURES)$df_ig
```

```{r, echo=FALSE}
result_ig_genRace <- informationGain_fs(df_diffRace_gen, NFEATURES)$result_ig
result_ig_methRace <- informationGain_fs(df_diffRace_meth, NFEATURES)$result_ig
result_ig_microRace <- informationGain_fs(df_diffRace_micro, NFEATURES)$result_ig

write.csv(result_ig_genRace[1:10, , drop = F], file = paste0(PLOTS_DIR, "result_ig_genRace.csv"), row.names = TRUE)
write.csv(result_ig_methRace[1:10, , drop = F], file = paste0(PLOTS_DIR, "result_ig_methRace.csv"), row.names = TRUE)
write.csv(result_ig_microRace[1:10, , drop = F], file = paste0(PLOTS_DIR, "result_ig_microRace.csv"), row.names = TRUE)

rm(df_diffRace_gen, df_diffRace_meth, df_diffRace_micro, df_diff_gen, df_diff_meth, df_diff_micro, result_ig_genRace, result_ig_methRace, result_ig_microRace)
```

## Data Analysis Information Gain Filter: Genomic Data

```{r, echo=FALSE}
print(colnames(df_ig_gen))
```

## Data Analysis Information Gain Filter: Genomic Data + Race

```{r, echo=FALSE}
print(colnames(df_ig_genRace))
```

## Data Analysis Information Gain Filter: Methylation Data

```{r, echo=FALSE}
print(colnames(df_ig_meth))
```

## Data Analysis Information Gain Filter: Methylation Data + Race

```{r, echo=FALSE}
print(colnames(df_ig_methRace))
```

## Data Analysis Information Gain Filter: Microbiome Data

```{r, echo=FALSE}
print(colnames(df_ig_micro))
```

## Data Analysis Information Gain Filter: Microbiome Data + Race

```{r, echo=FALSE}
print(colnames(df_ig_microRace))

rm(df_ig_microRace, df_ig_methRace, df_ig_genRace)
```
